Output Summary

### 2023-04-18 03-post-process/output-plots-children/06-length-based-survival.Rmd
Place boundaries on xlim for length-based survival

  # create vectors to predict survival at: for credible regions and mean curve
  L_Mb_seq = seq(min(L_Mb_lwr), max(L_Mb_upr), length = 30)
  L_Mb_star_seq = seq(min(L_Mb_star_lwr), max(L_Mb_star_upr), length = 30)

>>>>

  # create vectors to predict survival at: for credible regions and mean curve
  mean_diff = diff(range(L_Mb_mean)) * 0.1
  L_Mb_seq = seq(min(L_Mb_mean) - mean_diff, max(L_Mb_mean) + mean_diff, length = 30)
  L_Mb_star_seq = (L_Mb_seq - jags_data$L_Mb_center[j])/jags_data$L_Mb_scale[j]
